Random Forests", OAs

### 2023-11-17 src/la_RF.Rmd
oa.rf
ranger

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)

@@

## REPLACE WITH 0.1 INSTEAD OF OF 0 FOR THE GROWTH
df <- df %>% filter(!is.na(ladcd)) %>% 
  complete(ladcd, year) %>% 
  replace(is.na(.), 0)

@@

@@

@@

```{r}
library(caret)
library(randomForest)

# CV
tc <- trainControl(method = "cv",
                   number = 10,
                   savePredictions = 'final')

@@

for (t in years){
  tplus1 <- t + 1
  set.seed(71)
  model.all <- train(n ~ area + dist + dist.retail + London + south + #growth ~ 
                      n.slag + n.l.slag + n.nearest.city + year, #n.lag +
                     data = df %>% filter(year==t | year==tplus1), #%>% 
                       # mutate(growth = ifelse(growth == -Inf | growth == Inf, NA, growth)) %>% 
                       # mutate(growth = ifelse(is.na(growth), 0, growth)), 
                     #%>% mutate(growth = ifelse(growth== -Inf | growth == Inf, NA, growth))
                     trControl = tc,
                     method = "rf", #"rpart", # rf lm
                     na.action = na.omit,
                     preProc = c("center", "scale"),
                     importance = TRUE)
}

>>>>

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)

@@

# Complete panel
## REPLACE WITH 0.1 INSTEAD OF OF 0 FOR THE GROWTH
df <- df %>% filter(!is.na(ladcd)) %>% 
  complete(ladcd, year) %>% 
  replace(is.na(.), 0)

@@

#########CHECK 1:9################

@@

##############ADD EAST, 4 REGIONS IN TOTAL###########

@@

```{r}
# CV
tc <- trainControl(method = "cv",
                   number = 10,
                   savePredictions = 'final')

@@

for (t in years){
  tplus1 <- t + 1
  set.seed(71)
  model.all <- train(n ~ area + dist + dist.retail + London + south + #growth ~ 
                      n.slag + n.l.slag + n.nearest.city + year + n.lag,
                     data = df %>% filter(year==t | year==tplus1), #%>% 
                       # mutate(growth = ifelse(growth == -Inf | growth == Inf, NA, growth)) %>% 
                       # mutate(growth = ifelse(is.na(growth), 0, growth)), 
                     #%>% mutate(growth = ifelse(growth== -Inf | growth == Inf, NA, growth))
                     trControl = tc,
                     method = "ranger", #"rpart", # rf lm
                     na.action = na.omit,
                     #preProc = c("center", "scale"),
                     importance = 'impurity') # TRUE for rf
    assign(paste0("model.all",as.character(t + 1)), model.all)
}

### 2023-11-17 src/oa_RF.Rmd
ranger

# Complete panel
df <- df %>% filter(!is.na(oa11cd)) %>% 
  complete(oa11cd, year) %>% 
  replace(is.na(.), 0)

@@

@@

# Join with distance and area
df <- df %>% left_join(dist, by = c("oa11cd" = "oa11cd")) %>% 
  left_join(oa.gb@data, by = c("oa11cd" = "id")) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)

@@

```{r}
## THIS DROPS L999999... AND NI, WHICH NEEDS TO BE FIXED
df <- df %>% filter(!is.na(area))

# London = Islington 
oa.sf <- st_as_sf(oa.gb)
cities.sf <- st_as_sf(cities, coords = c("long", "lat"))
cities.sf <- st_set_crs(cities.sf, 4326)

help1 <- st_filter(oa.sf, cities.sf) %>% as_tibble %>% dplyr::select(id) %>% 
  left_join(df, by = c("id"="oa11cd")) %>% dplyr::select(id, year, n)

@@

dist <- dist %>% mutate(dist.city.name = names(.)[max.col(.[2:11]*-1)+1L])

@@

sf_use_s2(FALSE)
oa.c <- st_centroid(oa.sf)
kn <- knearneigh(oa.c, k = 5)
knn <- knn2nb(kn, row.names = NULL, sym = FALSE)
knn.l <- nb2listw(knn)

df <- df %>% drop_na() %>% 
  group_by(year) %>% 
  mutate(n.slag = lag.listw(knn.l, n)) %>% 
  group_by(oa11cd) %>% 
  mutate(n.l.slag = dplyr::lag(n.slag, n=1, order_by=year),
         n.lag = dplyr::lag(n, n=1, order_by = year)) %>% 
  left_join(help2, by = c("oa11cd" = "oa11cd"))

df <- df %>% left_join(df %>% dplyr::select(ladcd,year, n) %>% 
                         rename(n.nearest.city = n), 
                       by = c("nearest.city.LAD21CD" = "ladcd",
                              "year" = "year")) %>% 
  dplyr::select(-c(LAD21NMW, OBJECTID, BNG_E, BNG_N, LONG, LAT, SHAPE_Length)) %>% 
  relocate(LAD21NM, .after = ladcd)

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% dplyr::select(LAD21CD, RGN21CD)

df <- df %>% left_join(lookup.region, by = c("ladcd" = "LAD21CD")) %>% 
  relocate(RGN21CD, .after=year)

# North/South
#lookup.region %>% distinct(RGN21NM, .keep_all = T)
south <- c("E12000007", "E12000008", "E12000009" )
df <- df %>% mutate(south = ifelse(RGN21CD %in% south, 1, 0))

@@

## lisa maps

```{r}

sf_use_s2(FALSE)
la.c <- st_centroid(la.sf)
kn <- knearneigh(la.c, k = 5)
knn <- knn2nb(kn, row.names = NULL, sym = FALSE)
knn.l <- nb2listw(knn)

path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", n, "_oa") # for unique PC
#path.out <- paste0(path, "/outputs/lisa/lisa_level_pc", m, "_oa")  # for multiple PC

morani <- data.frame()

#spatial weight matrix
sf_use_s2(FALSE)
nb <- poly2nb(oa.gb)
listw <- nb2listw(nb, style = "W", zero.policy = T)

for (t in 1996:2012){
test <- oa.gb
test@data <- test@data %>% left_join(df[df$year==t,], by = c("id"="oa11cd")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),           # 0 for NAs and the same for year
         year = ifelse(is.na(year), t, year))

#spatial weight matrix
#moved out of the loop

#Moran's I
globalMoran <- moran.test(test$n, listw, zero.policy = T, na.action = na.exclude)
a <- cbind(globalMoran$estimate[[1]],globalMoran$p.value, t[1])
morani <- rbind(a, morani)

#LISA
lmoran<- cbind(test@data, localmoran(test$n, listw,  adjust.x=TRUE, zero.policy = T, na.action = na.exclude))
#lmoran

# centers the local Moran's around the mean
lmoran$Ii <- lmoran$Ii - mean(lmoran$Ii, na.rm = TRUE) 
lmoran$lag.n<-  lag.listw(listw,lmoran$n, NAOK = TRUE)

# centers the variable of interest around its mean

lmoran$ns <- lmoran$n - mean(lmoran$n, na.rm = TRUE) 
lmoran$lag.n <- lmoran$lag.n - mean(lmoran$lag.n, na.rm = TRUE)

signif <- 0.05
#lmoran

lmoran <- lmoran%>% 
  mutate(quadrant= ifelse(ns>0 & lag.n > 0, 1, 0)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.n < 0, 2, quadrant)) %>% 
  mutate(quadrant= ifelse(ns<0 & lag.n > 0, 3, quadrant)) %>% 
  mutate(quadrant= ifelse(ns>0 & lag.n < 0, 4, quadrant)) %>%   
  #mutate(quadrant= ifelse(lmoran$`Pr(z > 0)` > signif, 0, quadrant)) #%>% 
  mutate(quadrant= ifelse(lmoran$`Pr(z != E(Ii))` > signif, 0, quadrant)) #%>%

#   mutate(quadrant2= ifelse(ANC_st>0 & lagANC_st > 0, 1, 0)) %>% 
# mutate(quadrant2= ifelse(ANC_st<0 & lagANC_st < 0, 2, quadrant2)) %>% 
#   mutate(quadrant2= ifelse(ANC_st<0 & lagANC_st > 0, 3, quadrant2)) %>% 
#  mutate(quadrant2= ifelse(ANC_st>0 & lagANC_st < 0, 4, quadrant2)) %>% 
#  mutate(quadrant2= ifelse(lmoran$LISA_PANC > signif, 0, quadrant2))

mun_merge_new<- merge(test, lmoran, by="id")

# R p value map
breaks = c(0, 1, 2, 3, 4, 5)

cities <- maps::world.cities %>% 
  filter(country.etc=="UK") %>% 
  arrange(pop) %>% tail(10) 
tif_sf <- st_as_sf(cities, coords = c("long", "lat"), crs = 4326)

map <- tm_shape(mun_merge_new) + tm_fill(col = "quadrant", breaks = breaks, 
                                         palette = c("white","red","blue",
                                                     rgb(0,0,1,alpha=0.4),
                                                     rgb(1,0,0,alpha=0.4)), 
                                         labels = c("Not significant",
                                                    "High-High",
                                                    "Low-Low",
                                                    "Low-High",
                                                    "High-Low"), 
                                         title="LISA, websites per OA") + 
  tm_legend(text.size = 1) +
  #tm_scale_bar(position = c("LEFT", "BOTTOM"),text.size = 1.0)+
  #tm_compass(type = "8star",   position = c("RIGHT", "BOTTOM"),      show.labels = 2,   text.size = 0.5)+
  #tm_borders(alpha=.1) +
  tm_borders(lwd = 0) +
  tm_shape(gb, simplify = .2) + tm_borders(alpha=1, lwd = .7) +
  tm_shape(tif_sf) + tm_dots() + tm_text("name", size = .5) +
  tm_layout( frame = FALSE,  title = t) #"LISA with the R p-values ")
tmap_save(map, filename = paste(path.out, t, ".png", sep = ""))
}
```

Moran I

```{r}
path.out <- paste0(path, "/outputs/lisa/morani_oa.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

## Gini

```{r}

# add OAs with 0s
df.with0s <- df %>% mutate(country = substring(oa11cd, 1, 1)) %>%
  filter(country != "L" & country != "M" & country != "N") %>%
  filter(!is.na(country)) %>%
  complete(year, oa11cd, fill = list(n = 0)) %>%
  filter(year!=1000,
         !is.na(oa11cd)) %>%
  dplyr::select(-country)

gini.df <- data.frame()

for (t in 1996:2012){
    a <- df.with0s %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/lisa/gini_oa.csv")
gini.df %>% write_csv(path.out)
```

## Getis-Ord

```{r, eval = F}

t= 1998
local_g <- localG(OA.Census$Qualification, nb_lw)
local_g <- localG(df[df$year==t,]$n, listw)

local_g <- cbind(OA.Census, as.matrix(local_g))
names(local_g)[6] <- "gstat"

@@

## Panel regressions

```{r}
# London
model <- plm(log(n+0.001) ~ log(London+.001)*as.factor(year), 
             data = df,
             index = c("oa11cd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficients: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to London on website counts, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

# Cities
model <- plm(log(n+0.001) ~ log(dist+.001)*as.factor(year), 
             data = df,
             index = c("oa11cd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_cities_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficienst: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to Cities on website counts, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

# Retail centres
model <- plm(log(n+0.001) ~ log(dist.retail+.001)*as.factor(year), 
             data = df,
             index = c("oa11cd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_retail_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficients: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to Retail Centres on website counts, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)
```

## Website density regressions to London, cross-section

```{r}
dens.London <- data.frame()
out.model <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(London), data = df[df$year==t,]) 
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.London <- rbind(r2, dens.London)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.model <- rbind(out.model_, out.model)
}

names(dens.London)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/lisa/rsq_dist_london_oa.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

out.model <- out.model %>% 
  mutate(year = 1996:2012)

path.out <- paste0(path,"/outputs/lisa/b_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

r2.all <- dens.London %>% 
  rename(London = rsquared)

# Help for OA area size. I double checked the largest: E00102963
# It is correct, this is its size.
# ggplot(df, aes(x=area)) +
#     geom_histogram(binwidth=.5, colour="black", fill="white")
# 
# df %>% filter(area>50)
```

## Website density regressions to the nearest city, cross-section

```{r}
dens.distMet <- data.frame()
out.modelMet <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(dist), data = df[df$year==t,])
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.distMet <- rbind(r2, dens.distMet)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.modelMet <- rbind(out.model_, out.modelMet)
}

names(dens.distMet)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/lisa/rsq_dist_city_oa.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

out.modelMet <- out.modelMet %>% 
  mutate(year = 1996:2012)

path.out <- paste0(path,"/outputs/lisa/b_dist_city_oa.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

r2.all <- r2.all %>% left_join(dens.distMet) %>% 
  rename(cities = rsquared)
```

## Website density regressions to the nearest retail centre, cross-section

```{r}
dens.dist.retail <- data.frame()
out.model.retail <- data.frame()

for (t in 1996:2012){
  model <- lm(log(density+0.001) ~ log(dist.retail+0.001), data = df[df$year==t,]) 
  r2 <- as.data.frame(summary(model)$r.squared)
  r2$year = t
  dens.dist.retail <- rbind(r2, dens.dist.retail)

  out.model_ <- tidy(model, conf.int = TRUE) %>% 
    slice(2) %>% 
    mutate_if(is.numeric, round, 2)
  out.model.retail <- rbind(out.model_, out.model.retail)
}

names(dens.dist.retail)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/lisa/rsq_dist_centre_oa.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

out.model.retail <- out.model.retail %>% 
  mutate(year = 1996:2012)

path.out <- paste0(path,"/outputs/lisa/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) 
ggsave(path.out)

# library(pscl)
# m1 <- zeroinfl((n) ~ log(dist.retail+0.001),
#   data = df[df$year==t,], dist = "negbin", EM = TRUE)
# summary(m1)
# 
# df %>% filter(year == 1996) %>% 
#   group_by(group = cut(n, breaks = c(0, 1, 2, 10, 100, 1000, 10000), include.lowest = T, right = F)) %>%  #seq(0, max(n), 100))) %>%
#   summarise(n = sum(n))
```
All R^2 dataframe

```{r}
path.out <- paste0(path, "/outputs/lisa/r2_all_oa.csv")

r2.all <- dens.London %>% 
  rename(London = rsquared) %>% 
  left_join(dens.distMet) %>% 
  rename(cities = rsquared) %>% 
  left_join(dens.dist.retail) %>% 
  rename(retail = rsquared) %>% 
  relocate(year, .before = London) %>% 
  arrange(year)

write_csv(r2.all, path.out)
```

>>>>

# Partially complete panel as not all OAs have a website in at least ine year
df <- df %>% filter(!is.na(oa11cd)) %>% 
  complete(oa11cd, year) %>% 
  replace(is.na(.), 0)

@@

## Full panel

```{r}
oa.sf <- st_as_sf(oa.gb)

oa.full <- replicate(17, oa.sf %>% as_tibble(), simplify = FALSE) %>%
  bind_rows(.id = 'id_') %>% 
  rename(year = id_) %>% 
  mutate(year = as.numeric(year) + 1995) %>% 
  dplyr::select(id, year)

df <- oa.full %>% left_join(df, by = c("id" = "oa11cd", "year" = "year")) %>% 
  replace(is.na(.), 0)

sapply(df, function(x) sum(is.na(x)))
rm(oa.full)
```

@@

# Join with distance and area
df <- df %>% left_join(dist, by = c("id" = "oa11cd")) %>% 
  rename(oa11cd=id) %>% 
  left_join(oa.gb@data, by = c("oa11cd" = "id")) %>% 
  relocate(area, .after = n) %>% 
  mutate(area = area / 1000000,
         density = n / area) %>% 
  relocate(density, .after = area)

@@

```{r}
## THIS DROPS L999999... AND NI, WHICH NEEDS TO BE FIXED
#df <- df %>% filter(!is.na(area))

# London = Islington 
cities.sf <- st_as_sf(cities, coords = c("long", "lat"))
cities.sf <- st_set_crs(cities.sf, 4326)

# help1 <- st_filter(oa.sf, cities.sf) %>% as_tibble %>% dplyr::select(id) %>% 
#   left_join(df, by = c("id"="oa11cd")) %>% dplyr::select(id, year, n)

@@

# This efficiently returns the name of the column with the shortest distance
dist <- dist %>% mutate(dist.city.name = names(.)[max.col(.[2:11]*-1)+1L])

@@

#####save this#####
sf_use_s2(FALSE)
oa.c <- st_centroid(oa.sf)
kn <- knearneigh(oa.c, k = 5)
knn <- knn2nb(kn, row.names = NULL, sym = FALSE)
knn.l <- nb2listw(knn)
##################

df <- df %>% 
  group_by(year) %>% 
  mutate(n.slag = lag.listw(knn.l, n)) %>% 
  group_by(oa11cd) %>% 
  mutate(n.l.slag = dplyr::lag(n.slag, n=1, order_by=year),
         n.lag = dplyr::lag(n, n=1, order_by = year)) %>% 
  left_join(help2, by = c("oa11cd" = "oa11cd"))

df <- df %>% left_join(df %>% dplyr::select(oa11cd,year, n) %>% 
                         rename(n.nearest.city = n), 
                       by = c("nearest.city.oa11cd" = "oa11cd",
                              "year" = "year"))

# Lookup: OA to regions
path.lookup <- paste0(path, "/data/raw/Output_Area_to_Region_(December_2011)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% dplyr::select(OA11CD, RGN11CD, RGN11NM)

df <- df %>% left_join(lookup.region, by = c("oa11cd" = "OA11CD")) %>% 
  relocate(c(RGN11NM, RGN11CD), .after=year) %>% 
  mutate(help = substring(oa11cd, 1, 1),
         RGN11CD = ifelse(help=="E", RGN11CD,
                         ifelse(help=="W", "Wales",
                                ifelse(help == "S", "Scotland", NA))),
         RGN11NM = ifelse(help=="E", RGN11NM,
                         ifelse(help=="W", "Wales",
                                ifelse(help == "S", "Scotland", NA)))) %>% 
  dplyr::select(-help)

# df %>% ungroup() %>% distinct(RGN11NM)
# sapply(df, function(x) sum(is.na(x)))

# North/South
#lookup.region %>% distinct(RGN21NM, .keep_all = T)
south <- c("London", "South West", "South West", "East of England")
df <- df %>% mutate(south = ifelse(RGN11NM %in% south, 1, 0))

@@

## RF

### train on all but one regions

```{r}
out.path <- paste0(path, "/data/temp/oa_rf.RData")
# save.image(file = out.path)
start.time <- Sys.time()
load(out.path)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

unregister_dopar <- function() {
  env <- foreach:::.foreachGlobals
  rm(list=ls(name=env), pos=env)
}
unregister_dopar()

# CV
tc <- trainControl(method = "cv",
                   number = 10, #10,
                   allowParallel = T,
                   savePredictions = 'final')

# London region: E12000007

# detectCores()
# cl <- makePSOCKcluster(14)
# registerDoParallel(cl)

# train
start.time <- Sys.time()

set.seed(71)
m.test <- train(n ~ density + area + dist + dist.retail + London +
                  n.slag + year + n.nearest.city, #n.l.slag
                data = df %>% filter(RGN11CD=="E12000008"),
                trControl = tc,
                method = "ranger", #"rf", 
                importance = "impurity",  #TRUE,
                na.action = na.omit)

#stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

summary(m.test)
plot(m.test)
m.test
print(m.test)

varimp_mars <- varImp(m)
plot(varimp_mars, main="Variable Importance")
```

### test on the hold out regions

Wales region is missing!!!

```{r}
pred <- predict(m, df %>% ungroup() %>% filter(RGN21CD=="E12000008"), na.action = na.pass)
length(pred)

df %>% ungroup() %>% filter(RGN21CD=="E12000008") %>% filter(if_any(everything(), is.na))

pred <- cbind(pred %>% as_tibble(), df %>% ungroup() %>% filter(RGN21CD=="E12000008"))
postResample(pred = pred$value, obs = pred$n) ## 0.99
```

## RF rolling

### train the model in a loop

```{r}
# Train on t & t + 1

# Make the parallelisation reproducible using https://stackoverflow.com/questions/13403427/fully-reproducible-parallel-models-using-caret. 
# See also https://stackoverflow.com/questions/27944558/set-seed-parallel-random-forest-in-caret-for-reproducible-result

#length is = (n_repeats*nresampling)+1
seeds <- vector(mode = "list", length = 11)

#(8 is the number of tuning parameter, mtry for rf, here equal to ncol(iris)-2)
for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 9) # 9 after adding South

#for the last model
seeds[[11]]<-sample.int(1000, 1)

# CV
tc <- trainControl(method = "cv",
                   number = 10,
                   seeds = seeds,
                   allowParallel = T,
                   savePredictions = 'final')

detectCores()
cl <- makePSOCKcluster(14)
registerDoParallel(cl)

# run the model for every 2 years
start.time <- Sys.time()
years <- 1997:2012

for (t in years){
  tplus1 <- t + 1
  set.seed(71)
  model.all <- train(n ~ area + dist + dist.retail + London + south + #growth ~ 
                      n.slag + n.l.slag + n.nearest.city + year, #n.lag +
                     data = df %>% filter(year==t | year==tplus1), #%>% 
                       # mutate(growth = ifelse(growth == -Inf | growth == Inf, NA, growth)) %>% 
                       # mutate(growth = ifelse(is.na(growth), 0, growth)), 
                     #%>% mutate(growth = ifelse(growth== -Inf | growth == Inf, NA, growth))
                     trControl = tc,
                     method = "rf", #"rpart", # rf lm
                     na.action = na.omit,
                     preProc = c("center", "scale"),
                     importance = TRUE)
}

stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

# df %>% filter(growth == Inf) 
# log(n/n.lag)

# The loop creates: 1998 (train on 1997-1998) - 2013 (train on 2012)
# I need: 1998 (train on 1997-1998) - 2011 (train on 2010-2011)
```

### Resamples for plots

```{r}
# create a list of the above model outputs
fit.model.all <- mget(ls(pattern = "^model.all\\d"))

# resamples
fit.model.all.res <- resamples(fit.model.all)
summary(fit.model.all.res)

# plot metrics

# TODO: fix the year labels

scales <- list(x=list(relation="free"), y=list(relation="free"))
bwplot(fit.model.all.res, scales=scales)

# TODO: fix the year labels
```

### Variable importance

```{r , include=TRUE, results= 'markup', message=FALSE}
lapply(names(fit.model.all), function(x) plot(varImp(fit.model.all[[x]]), main=as.character(x)))
```

```{r}
help <- lapply(fit.model.all, function(x) varImp(x)) 
help <- lapply(help, function(x) x[[1]])
help <- do.call("rbind", help)

importance <- help %>% rownames_to_column() %>% 
  mutate(feature = gsub("model.all[0-9]+.", "", rowname),
         year = gsub(".*?([0-9]+).*", "\\1", rowname)) %>% 
  rename(importance = Overall) %>% 
  relocate(importance, .after = year) %>% 
  dplyr::select(-rowname)

importance %>% ggplot() +
  geom_line(aes(x=year, y = importance, color = feature, group = feature), size = 1) +
  scale_color_discrete(name = "Features") +
  #scale_linetype_manual(name = "Website density regressions111") 
  ylab("Importance") + 
  ggtitle("Feature importance") +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5))

@@

### test

```{r , include=TRUE, results= 'markup', message=FALSE, fig.height=15, fig.width=10}

# growth or n

# for a reference point
df %>% group_by(year) %>%
  summarise(min = min(n), max=max(n),
            mean = mean(n), median = median(n)) %>%
  round(2) %>% kable()
```

```{r}
## Test on t + 2

# It will create: 2001 (train on 2000-2001) - 2011 (train on 2010)
# I need: 2001 (train on 2000-2001) - 2009 (train on 2008-2009)

# use the model trainned in year t to predict io of year t + 1
years <- (1998:2011)
pred.by.year.all <- data.frame(matrix(NA,nrow=374, ncol = 0))
for (t in years){
  t_plus_1 <- t + 1
  pred <- predict(fit.model.all[names(fit.model.all)==paste0("model.all",t)], df[df$year==t_plus_1,])
  pred <- as.data.frame(pred)
  rownames(pred) <- c()
  pred.by.year.all <- cbind(pred.by.year.all, pred)
}

#change column names to match with total
names(pred.by.year.all) <- 1999:2012

# wide to long
pred.by.year.all <- gather(pred.by.year.all,key = year,value = predictions,1:14)

# drop 2000 and select variables form total
df.no1997_1 <- df %>% 
  filter(year!=1996 & year!=1997 & year!=1998) %>% 
  dplyr::select(ladcd, year, n) # CHANGE n WITH growth

# column bind prediction and data  
pred.by.year.all <- cbind(pred.by.year.all, df.no1997_1 %>% arrange(year, ladcd)) #DOUBLE CHECK ARRANGE

# pred.by.year to list by year
pred.by.year.all.list <- split(pred.by.year.all, pred.by.year.all$year)

# calculate metrics for every year
rf.year.all.metrics <- lapply(pred.by.year.all.list, function(x) postResample(pred = x$predictions,
                                                                     obs = x$n))  # CHANGE n WITH growth
rf.year.all.metrics %>% as.data.frame() %>%
  round(2) %>%
  kable()

# there are 2 columns named year, so I drop one
pred.by.year.all$year <- NULL

ggplot(data = pred.by.year.all,aes(x = n, y = predictions)) +
  geom_point(colour = "blue") +
  geom_abline(intercept = 0, slope = 1, colour = "red") +
  #geom_vline(xintercept = 23, colour = "green", linetype = "dashed") +
  facet_wrap(~ year,ncol = 2) +
  #coord_cartesian(xlim = c(0,50000),ylim = c(0,50000)) +
  ggtitle("Predicted vs. actual trade by year")
```
